Optimizing Scheduling Policies For Heterogeneous Distributed Systems

### 2020-02-20 phase2/report.tex
added team number
edited proposal references

\author{
   \begin{tabular}{c c c c}
       Mahmoud Adas & Evram Youssef & Mohamed Shawky & Remonda Talaat\\
       \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}} & \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}}
   \end{tabular}%
   \\
   \texttt{\small{\{mido3ds, evramyousef, mohamedshawky911, remondatalaat21\}@gmail.com}}
}%

\markboth{Cairo Uni. CMP Dep. OS, Research Phase 2, \today}{Shell}

@@

    \section{References}
    \subsection*{[1] Alexandru Iulian Orhean,  Florin  Pop, and Ioan Raicu. New scheduling approach using reinforcement learning for heterogeneous distributed systems. Journal of Parallel and Distributed Computing, 117:292–302, 2018.}
    \begin{itemize}
        \item Why this paper: So we get insights into how to use machine learning in achieving better scheduling policies.
        \item Paper research problem: Heterogeneous systems task scheduling problem.
        \item Paper goal: Determining a more efficient scheduling policy for heterogeneous systems.
        \item Tools: BURLAP library, Java RMI API, remote allocated schedulers and WorkflowSim.
        \item Conclusion: The paper proposed a platform of scheduling solutions as a service based on machine learning agents. 
        And found out a limitation with reinforcement learning approach. Which was that the system was incapable of learning optimal policy after adding many nodes.
    \end{itemize}

    \subsection*{[2] Rakesh Kumar, Er Rajiv Kumar, Er Sanjeev Gill, and Er Ashwani Kaushik. Genetic algorithm approach to operating system process scheduling problem. International journal of Engineering science and Technology, 2(9):4247–4252, 2010.}
    \begin{itemize}
        \item Why this paper: Because we plan to use GA as one of the methods of optimization, which what the paper used,
        even though the paper's target wasn't heterogeneous systems.
        \item Paper research problem: General-purpose OS task scheduling problem.
        \item Paper goal: Optimize scheduling parameters using GA.
        \item Conclusion: GA’s can provide a highly flexible and user-friendly, near optimal solution to the general job sequencing problem.
    \end{itemize}

    \subsection*{[3] Ashish Venkat and Dean M Tullsen. Harnessing isa diversity: Design  of  a  heterogeneous-isa  chip  multiprocessor. In 2014 ACM/IEEE 41st International Symposium on Computer Architecture(ISCA), pages 121–132. IEEE, 2014.}
    \begin{itemize}
        \item Why this paper: To understand heterogeneous systems structures.
        \item Paper research problem: Which one is more power effective, heterogeneous or homogeneous systems?
        \item Paper goal: prove heterogeneous systems are more power efficient
        \item Conclusion: heterogeneous systems improves energy efficiency over the most efficient single-ISA design by 23\%.
    \end{itemize} 
\end{document}

>>>>

\author{
   \small{Team 10}

   \begin{tabular}{c| c| c| c}
       Mahmoud Adas & Evram Youssef & Mohamed Shawky & Remonda Talaat\\
       \texttt{\small{SEC 2, B.N 21}} & \texttt{\small{SEC 1, B.N 9}} & \texttt{\small{SEC 2, B.N 16}} & \texttt{\small{SEC 1, B.N 20}}
   \end{tabular}%

   \texttt{\small{\{mido3ds, evramyousef, mohamedshawky911, remondatalaat21\}@gmail.com}}
}%

\markboth{Cairo Uni. CMP Dep. | OS Research | Phase 2 | Team 10 | \today}{Shell}

@@

    \section{References}
    \subsection*{[1] Ashish Venkat and Dean M Tullsen. Harnessing isa diversity: Design  of  a  heterogeneous-isa  chip  multiprocessor. In 2014 ACM/IEEE 41st International Symposium on Computer Architecture(ISCA), pages 121–132. IEEE, 2014.}
    \begin{itemize}
        \item Why this paper: To understand heterogeneous systems structures.
        \item Paper research problem: Which one is more power effective, heterogeneous or homogeneous systems?
        \item Paper goal: prove heterogeneous systems are more power efficient
        \item Conclusion: heterogeneous systems improves energy efficiency over the most efficient single-ISA design by 23\%.
    \end{itemize}

     \subsection*{[2] Padole, Dr. Mamta \& Shah, Ankit. (2018). Comparative Study of Scheduling Algorithms in Heterogeneous Distributed Computing Systems.}
    \begin{itemize}
        \item Why this paper: To understand the concepts and concerns of scheduling in heterogeneous systems, as well as the recent algorithms.
        \item Paper research problem: The recent scheduling algorithms for heterogeneous systems and their specifications.
        \item Paper goal: The paper offers a hierarchical view of the static and dynamic scheduling algorithms found by then and gives an brief overview for each one. 
        \item Conclusion: Most of the current scheduling algorithms can be further improved in various aspects, moreover static algorithms can be re-implemented to be dynamic.
    \end{itemize}

    \subsection*{[3] Arabnejad, Hamid \& Barbosa, Jorge. (2014). List Scheduling Algorithm for Heterogeneous Systems by an Optimistic Cost Table. IEEE Transactions on Parallel and Distributed Systems.}
    \begin{itemize}
        \item Why this paper: To get a sense of predictive scheduling in heterogeneous systems, as we will be using predictive models in our future work.
        \item Paper research problem: Task scheduling in heterogeneous systems based on Optimistic Cost Table (OCT).
        \item Paper goal: Achieve the same time complexity as the state-of-art methods, but with higher overall scheduling performance.
        \item Conclusion: Predictive-Earliest-Finish-Time (PEFT) is outperforms Heterogeneous-Earliest-Finish-Time (HEFT) with the same time complexity.
    \end{itemize} 
\end{document}
